---
author: "TJ Schaeffer"
title: "Homework 7"
date: "3/22/20"
output: html_notebook
---

```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(MASS)
library(car)
library(nortest)
library(dplyr)
library(ggplot2)
library(readr)
library(MuMIn)
# reading in data
bass <- read.csv("bass.csv")
```


1. Explanatory: Alkalinity
Response: Mercury

2.
```{r}
bass %>%
  ggplot(aes(x = Alkalinity, y = Mercury)) +
  geom_point()
```
Based off the graph, I do not believe the data meets the linearity assumption, but it seems to be independent and normally distributed, and the residuals look to be homoskedastic.

3. 
```{r}
fit <- lm(Mercury~Alkalinity, data = bass)
summary(fit)
```

4.
```{r}
bass %>%
  ggplot(aes(x = Alkalinity, y = Mercury)) +
  geom_point() +
  geom_smooth(method = 'lm', se = FALSE)
```
Based on the plot, it seems that a lake with 0 mg/l alkalinity contains .72 mg of Mercury and as the alkalinity of a lake increases by 1 mg/l, the amount of Mercury in that lake decreases by .005 mg. 

5.
```{r}
# Std Res
bass.studentres <- studres(fit)
bass.fittedvalues <- fit$fitted

plot(bass.studentres~bass.fittedvalues, ylab = "Standarized Residuals", xlab = "Fitted Values")
abline(h = 0, color = "azure4", lty = 2)

#Cook's Distance
plot(cooks.distance(fit), ylab = "Cook's Distance")
abline(h = 4/53, col = "red", lty = 2)
```

Based off the two plots, it seems that there a few residuals that are different from the rest of the data, proving my assumption that there is outliers in the data. 

6.
```{r}
plot(fit)
plot(hatvalues(fit)~bass$Alkalinity, type = "h", ylab = "Leverage")
abline(h=((2*2)/nrow(bass)), lty = "dotted")
```

The name of the lake with highest residual mercury value: Alligator
The name of the lake with highest leverage: Farm-14
The name of the lake with highest Cook’s distance: Puzzle

7. 
```{r}
influencePlot(fit)
```

I do not agree with this comment because based off the influence plot as well as the standard residual plot and the Cook's Distance plot, it seems to me that there is a least 4 points that are influential. 

8. Based off what we talked about in class, I would first start with transforming the explanatory variable and then if the adjusted R^2 value is too low, I would try transforming either just the response variable or possibly both to see what produces the highest adjusted R^2 value. 

9. 
```{r}
# Log transformation
logfit <- lm(Mercury~log(Alkalinity), data = bass)
summary(logfit)

# Sqrt transformation
sqrtfit <- lm(Mercury~sqrt(Alkalinity), data = bass)
summary(sqrtfit)
```
Pick: Log

10.
```{r}
AICc(logfit, sqrtfit)
```
Logfit seems to have a higher adjust R^2 value and has a lower AIC value.

11.
```{r}
# Log transformation plot
bass %>%
  ggplot(aes(x = Alkalinity, y = Mercury)) +
  geom_point() +
  geom_smooth(method = 'lm', formula = y~log(x), se = FALSE)
```

12. 
```{r}
#Cook's Distance
plot(cooks.distance(logfit), ylab = "Cook's Distance")
abline(h = 4/53, col = "red", lty = 2)

# High Leverage
plot(hatvalues(logfit)~bass$Alkalinity, type = "h", ylab = "Leverage")
abline(h=((2*2)/nrow(bass)), lty = "dotted")

# Normal Residual
plot(logfit)

# Std Red
bass.studentres2 <- studres(logfit)
bass.fittedvalues2 <- logfit$fitted
plot(bass.studentres2~bass.fittedvalues2, ylab = "Standarized Residuals", xlab = "Fitted Values")
abline(h = 0, color = "azure4", lty = 2)
```

13. 
```{r}
newlake <- data.frame(Alkalinity = 40)
predict(logfit, newdata = newlake, interval = 'prediction', level = 0.99)
```
No because the 99% prediction interval goes above 1mg of Mercury, meaning that there is a chance that a fish can contain more than 1 mg of Mercury.

14. 
```{r}
newlake2 <- data.frame(Alkalinity = 20)
predict(logfit, newdata = newlake2, interval = 'prediction', level = 0.95)
```

