---
title: "Homework 9"
author: "TJ Schaeffer"
date: "4/20/20"
output: 
  html_notebook:
  theme: united
  toc: yes
---

## Setup
```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(MASS)
library(car)
library(nortest)
library(dplyr)
library(ggplot2)
library(readr)
library(MuMIn)
library(corrplot)
library(lmtest)
library(StepReg)
# reading in data
movies <- read_csv("HollywoodMovies2011.csv")
```

## Question 1: Intial Analysis of Data
```{r}
# Mixed matrix scatter plot
plot(movies, main = "Scatter Plot Matrix")
```

```{r}
# Correlation plot
corrplot(cor(movies), method = "number")
```

## Question 2: Initial model
```{r}
# Creating fit1 and it's summary
fit1 <- lm(Profitability~RottenTomatoes+AudienceScore+TheatersOpenWeek+BOAverageOpenWeek+DomesticGross, data = movies)
summary(fit1)
```
Profitability = 5.42 + (0.07630)RottenTomatoes - (0.09577)AudienceScore - (0.0005657)TheatersOpenWeek -
(0.00003603)BOAverageOpenWeek + (0.02781)DomesticGross

## Question 3: Initial Model Analysis
At a 10% signifcance level, I would remove AudienceScore, TheatersOpenWeek and BOAverageOpenWeek from the model since their p-values are higher than the significance level. This does meet our expectations from the correlation plot because the variables we are removing had a correlation equal to or less than .1 in connection to the profability variable.

## Question 4: Second Model
```{r}
fit2 <-lm(Profitability~RottenTomatoes+DomesticGross, data = movies)
summary(fit2)
```
Profability = 0.836652 + (0.030925)RottenTomatoes + (0.016305)DomesticGross

## Question 5: Subsetted Tables
```{r}
# AIC Subset
output1 <- bestsubset(data=movies,y="Profitability",select="AIC",best = 5)
print(output1) 
```

```{r}
# Adjusted R-squared Subset
output2 <- bestsubset(data=movies,y="Profitability",select="adjRsq",best = 5)
print(output2)
```

```{r}
# BIC subset
output3 <- bestsubset(data=movies,y="Profitability",select="BIC",best = 5)
print(output3)
```

## Question 6: Goodness of Fit Analysis
Based on the analysis, the variables that are most important are AudienceScore and RottenTomatoes, as it is one of the two models with the lowest AIC/BIC and the highest adjusted R-square. The goodness of fit measure that I rely on the most is the adjusted R^2 because it traditionally gives the best relationship between the explanatory variables and the response. The best model is the one with AudienceScore and RottenTomatoes as the explanatory variables.

```{r}
# Creating and analyzing final fit
fit3 <- lm(Profitability~RottenTomatoes+AudienceScore, data = movies)
summary(fit3)
```
Profitability = 2.69669 + (0.05883)RottenTomatoes -(0.03523)AudienceScore

## Question 7: Final Fit Assumptions
```{r}
# Evaluating regression assumptions and multicollinearity
plot(fit3)
corr <- data.frame(movies$RottenTomatoes, movies$AudienceScore, movies$Profitability)
corrplot(cor(corr), method = "number")
```
To evaluate the linear assumptions, I used the plot() function to analyze the final fit model. Based off the residual plot, it seems that most of the residuals fall along the residual = 0 line and form a horizontal band around it, which I can then assume the model meets the the linearity and homoskedascity assumptions. Additionally, the residuals don't form a weird pattern, which I can then also assume that the model meets the independent assumption. Finally, the Q-Q plot shows that the model meets the normality assumption. 

As for the multicollinearity assumption, based off the correlation plot, none of the correlations seem to suggest that multicollinearity is not a factor in the model. 

## Question 8: Final Analysis
If I was talking to the TV reporter, I would say that the most important factors that impact profitability are the AudienceScore and the RottenTomatoes ratings of the movies. I believe this is because people are more likely to invest and see a movie with higher ratings from the people and critics who saw and rated the movie before them. My advice to directors who want their movies to have a high profitability would be to really produce a film that bolds well with the people and critics who post ratings online.
